A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Add BDDf function description

>>>>

The complete code of $\text{BDD}_f$ and $\text{BDD}_R$ is listed
in~\cite[p. 432]{BURCH90}. However, both functions are described briefly in the
following paragraphs.

In essence, $\text{BDD}_f \left( f, I_P \right)$ distinguishes between five cases
derived from the OBDD semantics and the $\mu$-Calculus, utilizing the graph-based
algorithms of Bryant~\cite{BRYANT86} (also see Section~\ref{sec:operations}) as
well as the $\text{BDD}_R$ function (for applying a relational term $R$) with a
subsequent substitution of the place-holders with the argument variables, i.e.
$\langle d_1 \leftarrow x_1, \ldots, d_n \leftarrow x_n \rangle$~\cite{BURCH90}.
